Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-22 latex/article.tex
URL
typo

Volumetric objects are being more and more popular in many
applications ranging from object modeling and rendering in Computer
Graphics to geometry processing in Medical Imaging or Material
Sciences. When considering large volumetric data, interactive
visualization of such images (or isovalue surfaces) is a complex
problem. Such issues become even more difficult when dynamic
volumetric datasets are considered. Beside such isosurface
visualization, we are also interested in performing geometry
processing on the digital object and to explore different parameter
settings of the geometry processing tool.  In this work, we focus on
interactive visualization of volumetric data isosurfaces combined with
a curvature tensor (mean/Gaussian curvature, principal curvatures
directions\ldots) estimation at each point of the digital
surface. Curvature maps on a given isosurface are key information when
exploring 3D structures in Material Sciences \todo{REF}. Furthermore,
since most curvature estimators require a parameter fixing the scale
to which the computation is performed. For short, such parameter
(integration radius, convolution kernel size, \ldots) specifies noise
level on the object surface. As a consequence, exploring interactively
different values of such parameter is mandatory.
\vspace{0.2cm}

\noindent\textbf{Contributions}\quad In this work, we propose a
framework to perform interactive visualization of complex 3D digital
structures combined with a dynamic curvature tensor estimation. More
precisely, we define a fully data parallel process on GPU hardware \todo{Definir GPU au cas ou ?} to
both efficiently extract adaptive isosurface and compute per vertex
curvature tensor using Integral Invariants estimators. Hence, this
system allows us to visualize curvature tensor in real-time on large
dynamic objects. Our approach combines a GPU implementation of
pointerless octrees to represent the data, an adaptive
viewpoint-dependent mesh extraction, and a GPU implementation of
integral invariant curvature estimations.

>>>>

Volumetric objects are being more and more popular in many
applications ranging from object modeling and rendering in Computer
Graphics to geometry processing in Medical Imaging or Material
Sciences. When considering large volumetric data, interactive
visualization of such images (or isovalue surfaces) is a complex
problem. Such issues become even more difficult when dynamic
volumetric datasets are considered. Beside such isosurface
visualization, we are also interested in performing geometry
processing on the digital object and to explore different parameter
settings of the geometry processing tool.  In this work, we focus on
interactive visualization of volumetric data isosurfaces combined with
a curvature tensor (mean/Gaussian curvature, principal curvatures
directions\ldots) estimation at each point of the digital
surface. Curvature maps on a given isosurface are key information when
exploring 3D structures in Material Sciences \todo{REF}. Furthermore,
most curvature estimators require a parameter fixing the scale
to which the computation is performed. For short, such parameter
(integration radius, convolution kernel size, \ldots) specifies noise
level on the object surface. As a consequence, exploring interactively
different values of such parameter is mandatory.
\vspace{0.2cm}

\noindent\textbf{Contributions}\quad In this work, we propose a framework to
perform interactive visualization of complex 3D digital structures combined with
a dynamic curvature tensor estimation. More precisely, we define a fully data
parallel process on GPU (Graphics Processor Unit) hardware to both efficiently
extract adaptive isosurface and compute per vertex curvature tensor using
Integral Invariants estimators. Hence, this system allows us to visualize
curvature tensor in real-time on large dynamic objects. Our approach combines a
GPU implementation of pointerless octrees to represent the data, an adaptive
viewpoint-dependent mesh extraction, and a GPU implementation of integral
invariant curvature estimators.
